Pillar 1 - Sequential Pattern Mining

### 2019-03-13 Pillar 1 - Sequential Pattern Mining.Rmd
simplify computation of d_support$TNT
base computation of d_support$TNT on transcript_augmented instead of transactions (more appropriate)

First we transform our data into transaction data. For this, we first create a vector of mandatory courses that we exclude from transcripts. 
## Data Preparation

@@

## Support
```{r}
d_support <- list()

# Probability of taking a course
d_support$TNT <- d_transactions$taken_PF_HL %>%
  distinct(
    item,
    sequenceID
    ) %>%
  count(
    item
    ) %>%
  mutate(
    rate.take = n / n_students,
    rate.not  = 1 - rate.take
    )

#
# Probability of failing, having a low grade
d_support$PF_HL <- d_transactions$taken_PF_HL %>%
  group_by(
    item
    ) %>%
  summarise(
    rate.fail = mean(PF == "fail"),
    rate.low  = mean(HL == "low")
    )

>>>>

First we transform our data into transaction data. For this, we first create a vector of mandatory courses that we exclude from transcripts.

## Support

```{r d_support TNT}
d_support <- list()

# Probability of taking a course
d_support$TNT <- d_transcript_augmented %>%

  group_by(`Course ID`) %>%

  mutate(rate.take = n_distinct(`Student ID`) / n_students)
```

## Data Preparation

@@

## Support

```{r}
#
# Probability of failing, having a low grade
d_support$PF_HL <- d_transactions$taken_PF_HL %>%
  group_by(
    item
    ) %>%
  summarise(
    rate.fail = mean(PF == "fail"),
    rate.low  = mean(HL == "low")
    )
